---
title: "17 Classifications of Car Data" 
author: "Autoz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options:
  chunk_output_type: console
output:
  html_document:
    toc: yes
---

> originated by Car Evaluation Analysis - Suraj Vidyadaran

# Car Evaluation Analysis

17种分类 Car Data

## 1 Processing Data

```{r}
# 设置缓存
knitr::opts_chunk$set(cache = TRUE, autodep = TRUE)
# 批量必要环境,data.table高速读取几十万行数据
pacman::p_load(tidyverse,data.table,ggplot2,ggpubr,caret,gmodels,vcd)
```

> Car Data

```{r}
CAR <- read.csv("car.data.txt")
colnames(CAR)<-c("buying","maint","doors","persons","lug_boot","safety","class")
CAR$class = factor(CAR$class)
inTrain <- createDataPartition(y = CAR$class, p = 0.75, 
                               list = FALSE) # 75% training
CAR.train <- CAR[inTrain,]
CAR.test <- CAR[-inTrain,]
# formula
f_all <- as.formula(class ~ .)
f_6 <- as.formula(class~buying+maint+doors+persons+lug_boot+safety)
f_doors <- as.formula(class~doors)

rm(KA)
```


> Credit Data

```{r}
CRE <- read.csv("credit.csv")
CRE$default = factor(CRE$default)

inTrain <- createDataPartition(y = CRE$default, p = 0.75, 
                               list = FALSE) # 75% training
CRE.train <- CRE[inTrain,]
CRE.test <- CRE[-inTrain,]
```

## 2 Classification Analysis 分类
### A Linear Classification 线性分类
#### 1 Logistic Regression 逻辑回归

```{r,warning=FALSE,message=FALSE}
library(VGAM)

# Build the model
LR_fit <- vglm(f_all,family = multinomial,data = CAR.train)

#Predict using the model

probability <- predict(LR_fit,CAR.test,type="response") #概率
# probability <- predict(LR_fit,CAR.test[-7],type="response") #概率
# probability <- predictvglm(LR_fit,CAR.test,type="response")

pred_lr <-colnames(probability)[apply(probability,1,which.max)]

#Accuracy of the model

mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_lr))

confusionMatrix(mtab$actual, mtab$predict)$table

KA <- data_frame(Fit = "LR_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict))

# CrossTable(mtab$actual, mtab$predict,
#            dnn = c('actual', 'predicted'))
#            prop.chisq = F, prop.c = F, prop.r = F,
```

#### 2 Linear Discriminant Analysis 线性划分

```{r,warning=FALSE,message=FALSE}
library(MASS)

#Build the model
LDA_fit <- lda(f_all,data=CAR.train)

#Predict using the model
pred_lda<-predict(LDA_fit,CAR.test)$class

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_lda))

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "LDA_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))
```

### B Non-Linear Classification 非线性分类

#### 1 Mixture Discriminant Analysis 混合划分

```{r,warning=FALSE,message=FALSE}
library(mda)

#Build the model
MDA_fit<-mda(f_all,data=CAR.train)

#Predict using the model
pred_mda<-predict(MDA_fit,CAR.test)

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_mda))

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "MDA_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))

```

#### 2 Quadratic Discriminant Analysis 二次划分

> FALED with 矩阵不满秩 rank deficiency

```{r,warning=FALSE,message=FALSE}
library(MASS)

#Build the model
QDA_fit<-qda(f_doors,data=CAR.train)

#Predict using the model
pred_qda<-predict(QDA_fit,CAR.test)$class

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=pred_qda)

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "QDA_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))
````

#### 3 Regularized Discriminant Analysis 正则划分

````{r,warning=FALSE,message=FALSE}
library(klaR)

#Build the model
RDA_fit<-rda(f_all,data=CAR.train,gamma = 0.05,lambda = 0.01)

#Predict using the model
pred_rda<-predict(RDA_fit,CAR.test)$class

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=pred_rda)

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "RDA_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))
```

#### 4 Neural Network 神经网络
```{r,warning=FALSE,message=FALSE}
library(nnet)

#Build the model
NNET_fit<-nnet(f_all,data = CAR.train,
               size = 4,decay = 0.0001,maxit = 1000,trace=F)

#Predict using the model
pred_nnet<-predict(NNET_fit,CAR.test,type="class")

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_nnet))

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "NNET_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))

```

#### 5 Flexible Discriminant Analysis 灵活划分

```{r,message=FALSE,warning=FALSE}
library(mda)

#Build the model

FDA_fit<-fda(f_all,data=CAR.train)

#Predict using the model
pred_fda<-predict(FDA_fit,CAR.test,type="class")

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_fda))

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "FDA_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))
```

#### 6 Support Vector Machine 支持向量机

```{r,message=FALSE,warning=FALSE}
library(kernlab)

#Build the model
KSVM_fit <- ksvm(f_all,data=CAR.train)

#Predict using the model
pred_svm<-predict(KSVM_fit,CAR.test,type="response")

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_fda))

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "KSVM_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))
```

#### 7 k-Nearest Neighbors 近邻

```{r,message=FALSE,warning=FALSE}

#Build the model
KNN3_fit <- knn3(f_all,data=CAR.train,k=3)

#Predict using the model
pred_knn<-predict(KNN3_fit,CAR.test,type="class")

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_knn))

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "KNN3_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))
```

#### 8 Naive Bayes 贝叶斯分类

```{r,message=FALSE,warning=FALSE}
library(e1071)

#Build the model
NB_fit <-naiveBayes(f_all,data = CAR.train,k=5)

#Predict using the model
pred_naive<-predict(NB_fit,CAR.test)

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_knn))

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "NB_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))
```

### C Non-Linear Classification with Decision Trees 非线性分类树

#### 1 Classification and Regression Trees(CART) 回归树

```{r,message=FALSE,warning=FALSE}
library(rpart)

#Build the model
CART_fit<-rpart(f_all,data = CAR.train)

#Predict using the model
pred_cart<-predict(CART_fit,CAR.test,type="class")

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_knn))

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "CART_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))
```

#### 2 C4.5 决策树

```{r,message=FALSE,warning=FALSE}
library(RWeka)

#Build the model
C45_fit <- J48(f_all,data = CAR.train)

#Predict using the model
pred_c45<-predict(C45_fit,CAR.test)

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_knn))

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "C45_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))
```

#### 3 PART 部分决策树

```{r,message=FALSE,warning=FALSE}
library(RWeka)

#Build the model
PART_fit<-PART(f_all,data = CAR.train)

#Predict using the model
pred_part<-predict(PART_fit,CAR.test)

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_part))

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "PART_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))
```

#### 4 Bagging CART 背包回归树

```{r,message=FALSE,warning=FALSE}
library(ipred)

#Build the model
BAG_fit <- bagging(f_all,data = CAR.train)

#Predict using the model
pred_bag <- predict(BAG_fit,CAR.test)

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_bag))

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "BAG_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))
```

#### 5 Random Forest 随机森林

```{r,message=FALSE,warning=FALSE}
library(randomForest)

#Build the model
RF_fit <- randomForest(f_all,data = CAR.train)

#Predict using the model
pred_rf <- predict(RF_fit,CAR.test)

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_rf))

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "RF_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))
```

#### 6 Gradient Boosted Machine 梯度生成树机器

```{r,message=FALSE,warning=FALSE}
library(gbm)

#Build the model
GBM_fit <- gbm(f_all,data=CAR.train,
               distribution="multinomial",
               # cv.folds=5,
               shrinkage=0.1,
               interaction.depth = 16)

#Predict using the model
probability <- predict.gbm(GBM_fit,CAR.test,
                           n.trees = 100,
                           type='response')

pred_gbm<-colnames(probability)[apply(probability,1,which.max)]

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_gbm))

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "GBM_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))
```

#### 7 Boosted C5.0 生成树

```{r,message=FALSE,warning=FALSE}
library(C50)

#Build the model
C50_fit<-C5.0(f_all,data=CAR.train,
              trials=10)

#Predict using the model
pred_c50<-predict(C50_fit,CAR.test)

#Accuracy of the model
mtab <- data_frame(actual=CAR.test$class,
                   predict=factor(pred_c50))

confusionMatrix(mtab$actual, mtab$predict)$table

# MAd::Kappa(mtab$actual, mtab$predict)

KA <- KA %>% bind_rows(data_frame(Fit = "C50_fit",Kappa = MAd::Kappa(mtab$actual, mtab$predict)))
```

```{r}
arrange(KA,desc(Kappa))
```

